Black-hole ringdown as a probe of higher-curvature gravity theories

### 2022-04-04 papers/paper_alt_theor_bounds/paper_alt_theor_bounds.tex
hs: more editing on comp with gc

This means that using the $\pSEOB$ waveform model with theory-specific informed
QNMs we reduce the parameter space of beyond-GR parameters to $\ell$ alone.
%
We emphasize that our procedure is different from that of
Ref.~\cite{Carullo:2021dui} which, for a given value of $p$, varied all $\ell$,
$\delta\omega^{(n)}$, and $\delta\tau^{(n)}$ parameters, and then proceeded
to use the posteriors on $\ell$ to draw conclusions to any theory that predict
corrections at a given $p$.
%
This is a critical different between our study and Ref.~\cite{Carullo:2021dui}.
In particular, as we will see in Sec.~\ref{sec:results}, adding theory-specific
information to the ParSpec expansion \emph{can lead to different interpretation
of the final results, even for different theories which predict modifications
with the exponent $p$.}

>>>>

This means that using the $\pSEOB$ waveform model with theory-specific informed
QNMs we reduce the parameter space of beyond-GR parameters to $\ell$ alone.
%
We emphasize that our procedure is different from that of
Ref.~\cite{Carullo:2021dui} which, for a given value of $p$, varied all $\ell$,
$\delta\omega^{(n)}$, and $\delta\tau^{(n)}$ parameters, and then proceeded
to use the posteriors on $\ell$ to draw conclusions to any theory that predict
corrections at a given $p$.
%
This is a critical difference between our work and Ref.~\cite{Carullo:2021dui}.
In particular, as we will see in Sec.~\ref{sec:results}, adding theory-specific
information to the ParSpec expansion coefficients \emph{can lead to different interpretations
of the final bounds on $\ell$, even for different theories which predict value of the exponent $p$.}
